---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hmcdm

<!-- badges: start -->
[![Build Status](https://travis-ci.com/tmsalab/hmcdm.svg)](https://travis-ci.com/tmsalab/hmcdm)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN Version Badge](http://www.r-pkg.org/badges/version/hmcdm)](https://cran.r-project.org/package=hmcdm)
[![CRAN Status](https://cranchecks.info/badges/worst/hmcdm)](https://cran.r-project.org/web/checks/check_results_hmcdm.html)
[![RStudio CRAN Mirror's Monthly Downloads](http://cranlogs.r-pkg.org/badges/hmcdm?color=brightgreen)](http://www.r-pkg.org/pkg/hmcdm)
[![RStudio CRAN Mirror's Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/hmcdm?color=brightgreen)](http://www.r-pkg.org/pkg/hmcdm)
[![Coverage test coverage](https://codecov.io/gh/tmsalab/hmcdm/branch/master/graph/badge.svg)](https://codecov.io/github/tmsalab/hmcdm?branch=master)
<!-- badges: end -->

The goal of `hmcdm` is to provide an implementation of Hidden Markov Cognitive Diagnosis Models for Learning.

## Installation

You can install `hmcdm` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("hmcdm")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/hmcdm")
```

## Usage

To use `hmcdm`, load the package using:

```{r example}
library("hmcdm")
```


## Authors

Susu Zhang, Shiyu Wang, and Yinghan Chen

## Citing the `hmcdm` package

To ensure future development of the package, please cite `hmcdm`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("hmcdm")
```

## License

GPL (>= 2)