---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hmcdm

<!-- badges: start -->
[![R build status](https://github.com/tmsalab/hmcdm/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/hmcdm/actions)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
<!-- badges: end -->

The goal of `hmcdm` is to provide an implementation of Hidden Markov Cognitive Diagnosis Models for Learning.

## Installation

You can install `hmcdm` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("hmcdm")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/hmcdm")
```

## Usage

To use `hmcdm`, load the package using:

```{r example}
library("hmcdm")
```

## Authors

Susu Zhang, Shiyu Wang, and Yinghan Chen

## Citing the hmcdm package

To ensure future development of the package, please cite `hmcdm`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("hmcdm")
```

## License

GPL (>= 2)

